Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits

### 2022-11-21 04_paper/1118_final.Rmd
hot off the press

Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012]. Similarly, in terms of where China's money goes and its economic influences concentrate, some countries clearly are more important than others. However, Beijing holds the reasons why close to the vest.

The secrecy surrounding China's international development financing is puzzling. But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017]. In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, much like these traditional donors, Like traditional Western donors, foreign aid provision is a foreign policy tool to boost the status of the donor country [@ferry_turning_2021]. China's foreign aid can present as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation. In contrast, while arguably China's economic interests seem to play a central role in its allocation of foreign financing activities, empirical evidence does not show associations between Chinese foreign aids and a country's natural resource endowments [@hendrix_confronting_2014; @dreherFuchs2015].

@@

We propose that despite the lack of formal reporting, Beijing's overseas financing allocations go hand in hand with its focus on building allies and shaping foreign public opinions. Specifically, we consider foreign policy tools such as outward-facing state-sponsored news coverage and bilateral diplomatic visits from Beijing. While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomatic visits and media coverage are critical *visible* activities that can promote the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we expect that in general, recipients of China's overseas development assistance will also attract disproportionate attention of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.

As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals [@dreherEtAl2018]. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender. We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intention as a profit-seeking lender. Hence, we develop more fine-grained hypotheses: Aid recipient countries receive more media coverage and diplomatic visits from China, while debt recipient countries do not.

@@

To foreshadow our results, we find that there are very few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time. In other words, China targets its aid and debt to different sets of developing countries. However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as the conventional view holds. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomatic visits with its debtors.

On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs. Notably, *Xinhua*'s new stories do not just promote China's efforts to offer aid to those countries in need but also give a rounded picture of those countries' economic conditions justifying their legitimate need for aid. On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors. These findings contradict with what conventional views hold that Beijing has tried to keep its financial assistance secret. Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid recipients. It helps to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.

Furthermore, in contrast to what conventional wisdom holds, China does not shy away from its ambition in building closer bilateral cooperation with its debt recipients to align with their foreign policy goals. In addition to lending money, China engages in building and strengthening long-term bilateral relationships with these countries. Foreign policy goals play a central role in motivating Beijing's debt allocations. Meanwhile, our finding that Chinese loans corresponding with its diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI). A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance  ---  China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions. Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a popularly constructed meme based on collective fear of the Chinese threat rather than sound empirical evidence. Our empirical finding suggests that China is more likely to provide loans to diplomatically aligned countries. For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017. In contrast, Iraq shows the opposite pattern: it receives the highest amount of need-based aid from China during the period of our investigation, but it does not receive any loans. Concerns about Chinese debt nonetheless raise a natural question related to the function of diplomacy in debtor countries. Our findings suggest that China's international development program is complex and multifaceted. Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins? Our study sheds some new light on this pressing question, but further research is needed to fully answer it.

This paper proceeds as follows. We start by outlining different motivations for China's state financing allocations, followed by discussions of possibly using state-sponsored media and diplomatic visits for Chinese international recognition. We then introduce the variables and model specification strategies in the methods section. Before we show the results from our models, we provide several figures to present our descriptive analysis. Finally, we present our results, with conditional support of our hypotheses, and end with discussions on the implications of our findings.

@@

Two waves of surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^2] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments. Like the major Western powers, donors of foreign aid is status-conferring: it demonstrates a dedication to helping the needed, improving the audiences' perception of the donor [@goldsmith_doing_2014; @ferry_turning_2021].

@@

Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid. In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives. We focus in particular on two factors:  (1) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences) and (2) elite level diplomatic visits from China to developing countries. We propose that countries receiving disproportionately China’s bilateral development finance support also receive more concentrated media coverage and diplomatic visits from Beijing.

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans [@dreher_banking_2022].

@@

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972]. More specifically, as Lang and Lang [-@berelson_mass_1966] observe, "The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public.

Over decades of rich research in agenda-setting, empirical patterns support Cohen [-@cohen_press_1963] 's famous notation that the media is "stunningly successful in telling its readers what to think about" (p. 13; *emphasis added*). That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972]. Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn, shapes individuals' perceptions of the relative importance and salience of the issues.

To extend this logic, media salience indicates significance for foreign countries named in the media. Wanta et al. [-@wanta_agenda_2004-3] show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S. The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.

With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention. From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover. Not all countries in the world receive equal coverage. In fact, only a small portion of international events can get through the media gatekeepers and get media coverage. While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. Golan and Wanta's [-@golan_international_2003-1] study examines how 138 elections held between 1998 and 2000 were covered by the U.S. network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage [@sheafer_relative_2014-1]. Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.

@@

In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences. Nye [-@nye_public_2008-2] suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power". Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press. China has expanded its Xinhua News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.

Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others [@entman_theorizing_2008; @kiousis_international_2008]. Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes. Improving one's image to foreign audiences is the core objective of mediated public diplomacy.

As a state-sponsored media platform, Xinhua News Agency is often considered more than a news media agency. *Xinhua* is firmly under the control of the CCP's Central Propaganda Department. In 2013, President Xi Jinping exhorted the Propaganda Department to "tell Chinese stories well," and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013]. It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1], with an increasingly global reach to produce millions of articles in the past decade with hundreds of bureaus worldwide. Yet, *Xinhua*'s news reports should not be dismissed as mere propaganda or empty slogans. *Xinhua* presents itself as a balanced and fact-based news agency, not a government mouthpiece [@brazys_chinas_2020]. It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format. This outward-facing Chinese official media, whose mission as a key disseminator of the Party's narrative to foreign audiences, may inform us of the PRC government's initiatives of presenting Chinese perspectives of real-time events to global audiences. Governments use media to tell its story to the world and improve its public relations with other countries. As such, scholars often focus on Chinese mediated public diplomacy efforts through Xinhua. That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009].

@@

This paper will focus on Xinhua outward-facing English branch whose audiences are primarily English-speaking readers. Simply providing more information will not improve their image in the Western world. Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack. As Druckman [-@druckman_limits_2001] presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.

Hence, while Xinhua plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of Xinhua to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, p. 4]. In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" [@deibel_culture_1976, p. 15].

@@

Government-to-government visits are an indicator of the importance the Chinese government places on developing relations with a country as leaders' resources are scarce [@kastner_is_2012]. These visits have both symbolic and functional roles. Diplomatic visits often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005]. In fact, studies show that diplomatic visits of Chinese leaders lead to stronger commercial ties and surge of investment [@stone_chinese_2022]. For example, Chinese President Xi Jinping promised over 10 billion of investment during a state visit to South Africa. In a news conference hosted by President Cyril Ramaphosa, he demonstrated that “We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties” [@reuter_chinas_2018]. The high-profile leader visits are even used as a proxy for Chinese favor-giving and lobbying for votes in the UN [@wang_leader_2022]. Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018]. In all, diplomatic visits send an important positive signal that the visiting and hosting countries support each other and have close long-term relationships.

@@

To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing. We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships. As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its commercial goals. The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China. However, an examination of patterns in the main variables of interest in this study questions this tidy distinction. We therefore expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.

@@

To test hypotheses 1-4, we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively. Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process. We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means. We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values. Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.

@@

| Variables       | Definitions          | Sources           |
|------------------|------------------------------------------------|--------------|
| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country. | Global News Archive[^8]|
| `Diplomatic visits`      | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.| China's Global Public Diplomacy[^9]|
| `Aid`     | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year. | Chinese Development Finance[^10]|
| `Debt` | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.         | Chinese Development Finance|
| `UN Vote Agreement (distance)` | Aggregated distance of ideal points of UN General Assembly Voting by year        | UN General Assembly Voting Data[^11] |
| `GDP` | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$)        | World Bank[^12]|
| `Population` | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship.        | World Bank|
| `Disaster` | Deaths as a result of natural disasters in recipient countries by year        | Global Burden of Disease Study [^13]|
| `Civil wars` | State-based violent conflicts count of the recipient countries by year        | PRIO Conflict Recurrence Database[^14]|
| `Distance` | Bilateral country distances between recipient countries and China        | CEPII[^15]|
| `Export/Import` | Annual trade statistics between recipient countries and China        | Open Trade Statistics[^16]|
| `FDI` | Foreign direct investment to the recipient countries, net (BoP, current US$) by year       | World Bank|
| `Democracy Score` | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?      | V-Dem[^17]|

[^7]: Selecting news articles' headlines that mention one or more of these keywords: aid, donor, lend, development, investment, growth, support, business, help, construction, education, funds, projects, donate, assist
[^8]: @cline_center_for_advanced_social_research_global_2022
[^9]:  @aiddata_aiddata_2021
[^10]: @custer_tracking_2021
[^11]: @voeten_united_2009
[^12]: @world_bank_world_2022
[^13]: @health_metrics_and_evaluation_ihme_global_2019
[^14]: @uppsala_conflict_data_program_ucdp_prio_2020
[^15]: @mayer_notes_2011
[^16]: @vargas_open_2022
[^17]: @coppedge_v-dem_2020

>>>>

Despite the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017]. In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared. Instead, like traditional Western donors, Beijing uses foreign aid as a foreign policy tool to accomplish goals like boosting its international status and realizing diplomatic objectives in recipient countries [@ferry_turning_2021].

@@

We propose that Beijing's overseas financing goes hand in hand with other visible activities. Specifically, we consider foreign policy tools such as outward-facing state-sponsored news coverage and bilateral diplomatic visits from Beijing. While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomatic visits and media coverage are critical *visible* activities that can promote the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we expect that in general, recipients of China's overseas development assistance will also attract disproportionate attention of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.

In our analysis we leverage the latest data on China's overseas development financing produced by AidData, in addition to two other relatively new databases. For *Xinhua* articles, we rely on the new Archer web portal from the Cline Center for Advanced Social Research at the University of Illinois at Urbana-Champaign, which makes accessible the vast Global News Index compiled by the Cline Center. For diplomatic visits, we take advantage China's Public Diplomacy Dashboard recently compiled by AidData.

As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals [@dreherEtAl2018]. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender. We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intentions as a profit-seeking lender. Hence, we develop more fine-grained hypotheses: Aid recipient countries receive more media coverage and diplomatic visits from China, while debt recipient countries do not.

@@

To foreshadow our results, we find that there are very few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time. In other words, China targets its aid and debt to different sets of developing countries. However, statistical tests show that the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercially oriented ones, as the conventional view holds. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomatic visits with its debtors.

This paper proceeds as follows. We start by outlining different motivations for China's overseas financing, followed by discussions of state-sponsored media and diplomatic visits. We then introduce the variables and model specification strategies in the methods section. Before we show the results from our models, we provide several figures to present our descriptive analysis. Finally, we present our results, with conditional support of our hypotheses, and end with discussions on the implications of our findings.

@@

Two waves of surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^2] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments. And, beyond generating goodwill, giving aid also has been shown to be related to status in the international system as well[@ferry_turning_2021]---another fact that is surely not lost on policymakers in Beijing.

@@

Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid. In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives. We focus in particular on two factors: (1) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences) and (2) elite level diplomatic visits from China to developing countries. We propose that countries receiving disproportionately China's bilateral development finance support also receive more concentrated media coverage and diplomatic visits from Beijing.

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans [@dreher_banking_2022].

@@

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of issues based on the amount of coverage that those issues receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972]. More specifically, as Lang and Lang [-@berelson_mass_1966] observe, "The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public.

Over decades of rich research in agenda-setting, empirical patterns support Cohen's [-@cohen_press_1963] famous line that the media is "stunningly successful in telling its readers what to think about" (p. 13). That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972]. Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn, shapes individuals' perceptions of the relative importance and salience of the issues.

To extend this logic, media salience indicates significance for foreign countries named in the media. Wanta et al. [-@wanta_agenda_2004-3] show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S. Media coverage of certain countries will lead to these countries becoming more salient among the public.

The news editor is a key source of gatekeeping power since they can tell us where to focus our attention. From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

Also, previous findings show the strategic consideration of news editors in considering what international news gets media coverage. Not all countries in the world receive equal coverage. In fact, only a small portion of international events can get through the media gatekeepers and get media coverage. While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. Golan and Wanta's [-@golan_international_2003-1] study examines how 138 elections held between 1998 and 2000 were covered by the U.S. network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage [@sheafer_relative_2014-1]. Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.

@@

In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences. Nye [-@nye_public_2008-2] suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power". Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press. China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.

Recent research on second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes over others [@entman_theorizing_2008; @kiousis_international_2008]. Compared to first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes. Improving one's image to foreign audiences is the core objective of mediated public diplomacy.

As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency. *Xinhua* is firmly under the control of the CCP's Central Propaganda Department. In 2013, President Xi Jinping exhorted the Propaganda Department to "tell Chinese stories well," and the *Xinhua* news agency is at the forefront [@xinhua_xi_2013]. It has had a dual role: reporting news and building up China's image as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1], with an increasingly global reach and ability to produce millions of articles in the past decade with hundreds of bureaus worldwide. Yet, *Xinhua*'s news reports should not be dismissed as mere propaganda or empty slogans. *Xinhua* presents itself as a balanced and fact-based news agency, not a government mouthpiece [@brazys_chinas_2020]. It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence overseas. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more viewer-friendly format.

This outward-facing Chinese official media, whose mission as a key disseminator of the Party's narrative to foreign audiences, may inform us of the PRC government's initiatives of presenting Chinese perspectives of real-time events to global audiences. Governments use media to tell its story to the world and improve its public relations with other countries. As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*. That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009].

@@

This paper will focus on *Xinhua*'s outward-facing English branch whose audiences are primarily English-speaking readers. Simply providing more information will not improve their image in the Western world. Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack. As Druckman [-@druckman_limits_2001] presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage, and they should be consistent with the high officials' visions.

@@

Previous sections illustrate media agenda-setting as an essential step in Beijing's efforts to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, p. 4]. In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" [@deibel_culture_1976, p. 15].

@@

Government-to-government visits are an indicator of the importance the Chinese government places on developing relations with a country as leaders' resources are scarce [@kastner_is_2012]. These visits have both symbolic and functional roles. Diplomatic visits often mark further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005]. In fact, studies show that diplomatic visits of Chinese leaders lead to stronger commercial ties and surge of investment [@stone_chinese_2022]. For example, Chinese President Xi Jinping promised over \$10 billion of investment during a state visit to South Africa. In a news conference hosted by President Cyril Ramaphosa, he demonstrated that "We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties" [@reuter_chinas_2018]. The high-profile leader visits are even used as a proxy for Chinese favor-giving and lobbying for votes in the UN [@wang_leader_2022]. Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018]. In all, diplomatic visits send an important positive signal that the visiting and hosting countries support each other and have close long-term relationships.

@@

To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing. We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships. As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its commercial goals. The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China. We therefore expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.

@@

To test hypotheses 1-4, we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively. Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process. We opt for negative binomial regression rather than Poisson since we do not wish to impose assumptions about whether the variance of the outcomes is equivalent to their means. We further apply a zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values. Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.

@@

| Variables                         | Definitions                                                                                                                                                      | Sources                                |
|----------------|----------------------------------------|----------------|
| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country.                                                      | Global News Archive[^8]                |
| `Diplomatic visits`               | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.                                | China's Global Public Diplomacy[^9]    |
| `Aid`                             | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year.                                                 | Chinese Development Finance[^10]       |
| `Debt`                            | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.                                                            | Chinese Development Finance            |
| `UN Vote Agreement (distance)`    | Aggregated distance of ideal points of UN General Assembly Voting by year                                                                                        | UN General Assembly Voting Data[^11]   |
| `GDP`                             | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$) | World Bank[^12]                        |
| `Population`                      | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship. | World Bank                             |
| `Disaster`                        | Deaths as a result of natural disasters in recipient countries by year                                                                                           | Global Burden of Disease Study [^13]   |
| `Civil wars`                      | State-based violent conflicts count of the recipient countries by year                                                                                           | PRIO Conflict Recurrence Database[^14] |
| `Distance`                        | Bilateral country distances between recipient countries and China                                                                                                | CEPII[^15]                             |
| `Export/Import`                   | Annual trade statistics between recipient countries and China                                                                                                    | Open Trade Statistics[^16]             |
| `FDI`                             | Foreign direct investment to the recipient countries, net (BoP, current US\$) by year                                                                            | World Bank                             |
| `Democracy Score`                 | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?                                                                    | V-Dem[^17]                             |

[^7]: Selecting news articles' headlines that mention one or more of these keywords: aid, donor, lend, development, investment, growth, support, business, help, construction, education, funds, projects, donate, assist

[^8]: @cline_center_for_advanced_social_research_global_2022

[^9]: @aiddata_aiddata_2021

[^10]: @custer_tracking_2021

[^11]: @voeten_united_2009

[^12]: @world_bank_world_2022

[^13]: @health_metrics_and_evaluation_ihme_global_2019

[^14]: @uppsala_conflict_data_program_ucdp_prio_2020

[^15]: @mayer_notes_2011

[^16]: @vargas_open_2022
